Data Responsive-report

### 2021-02-25 GALI_2020.Rmd
This is a long due commit after running analysis and moving things to papaja

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

#X countries have fewer than 70 firms in the sample. Because so few observations may not offer good representation, I excluded firms headquartered in these countries from the analysis, keeping X firms in Y countries and Z industries.

@@

countries_to_keep <- filter(countries_to_keep, Count >6)
countries_to_keep$`gali$info_venture_country_hq`

@@

#Keep only ventures with 3 years of post acceleration information 
gali <- filter(gali, fu1report_followup_yes == 1 & fu2report_followup_yes == 1 & fu3report_followup_yes == 1)

@@

countries_to_keep <- filter(countries_to_keep, Count >6)
countries_to_keep$`gali$country`

@@

#Normalize NES data (all data is based on a scale from 1 to 5)
preproc_nes <- preProcess(gem_nes[,(4:5)], method=c("range"))

gem_nes <- predict(preproc_nes, gem_nes)

@@

gci <- filter(gci, `Series Global ID` == "EOSQ089" |
                   `Series Global ID` == "EOSQ425" |
                   `Series Global ID` == "EOSQ109")
gci <- filter(gci, Edition ==2018 )

@@

gci <- gci %>%
  pivot_wider(names_from = series_global_id, 
              values_from = score)

#preproc_gci <- preProcess(gci %>%
#                           select(starts_with("EOSQ"))
#                          , method=c("range"))
#gci <- predict(preproc_gci, gci)

#gci$inst_fc_gci <- rowMeans(gci[,c('EOSQ425','EOSQ089')], na.rm = TRUE)

#gci$inst_sc_gci <- gci$EOSQ109

#gci <- select(gci, !starts_with('EOSQ'))

@@

```{r}
#Rank 1 shows the most important benefit (highest attention)

#Normalize Attention data (all data is based on a scale from 1 to 7)
preproc_gali <- preProcess(gali %>%
                            select(starts_with("accel_ben_rank_"))
                          , method=c("range"))
gali <- predict(preproc_gali, gali)

@@

gali$attention_hc <- 1- round(gali$accel_ben_rank_business_skills,2)

gali$attention_signaling <- 1- round((gali$accel_ben_rank_aware_cred),2)

gali$attention_sc <- 1- round((rowMeans(gali[,
                                  c('accel_ben_rank_network',
                                'accel_ben_rank_access_entreprene',
                                'accel_ben_rank_access_investors')],
                              na.rm=TRUE)),2)

gali$attention_fc <- 1- round(gali$accel_ben_rank_direct_funding,2)

@@

#Join all 3 datasets 
```{r}
gali_joined <- left_join(gali, gem, by = c("country", "year"))

gali_joined <- left_join(gali_joined, gci, by = "country")

@@

#Mixed model analysis 
```{r}
fit0 <- lmer(capital_raised_tot ~  attention_fc + (attention_fc|country), data = gali_joined, REML = F)

fit1 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*EOSQ425 + (1 |country), data = gali_joined, REML = F)

fit2 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*EOSQ089 + (1 |country), data = gali_joined, REML = F)

fit3 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*inst_fc_gem + (1 |country), data = gali_joined, REML = F)

summary(fit2)

@@

#Exploring with plots
```{r}
ggplot(gali_joined, aes(inst_hc_gem,inst_fc_gem)) +
  geom_point()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("devtools")
#devtools::install_github("crsh/papaja")
```

@@

#X countries have fewer than 50 firms in the sample. Because so few observations may not offer good representation, I excluded firms headquartered in these countries from the analysis, keeping X firms in Y countries and Z industries.

@@

countries_to_keep <- filter(countries_to_keep, Count >9)
countries_to_keep$`gali$info_venture_country_hq`

@@

#Keep only for porfit firms 
gali <- filter(gali, info_legal_status == "For-profit company" )

@@

countries_to_keep <- filter(countries_to_keep, Count >9)
countries_to_keep$`gali$country`

@@

#Normalize NES data (all data is based on a scale from 1 to 5)
mean_norm_minmax <- function(x){
                                (x- mean(x)) /(max(x)-min(x))
                               }

mean_norm_nes <- as.data.frame(lapply(gem_nes[,(4:5)], mean_norm_minmax))

gem_nes <- cbind(gem_nes[, (1:3)], mean_norm_nes)

@@

gci <- filter(gci, `Series Global ID` == "EOSQ089" |
                   `Series Global ID` == "EOSQ425" |
                   `Series Global ID` == "EOSQ109" |
                   `Series Global ID` == "DOMCREDITGDP" |
                   `Series Global ID` == "EOSQ403")
gci <- filter(gci, Edition ==2018 )

@@

gci <- gci %>%
  pivot_wider(names_from = series_global_id, 
              values_from = score)
```

#Plotting all countries along the 3 dimensions

```{r fig.height=10, fig.width=10}

library(plot3D)

with(gci, text3D(EOSQ403, EOSQ425, EOSQ109, 
  labels = gci$country,  
  col = gg.col(100), theta = 60, phi = 20,
  xlab = "Human capital", ylab = "Financail capital", zlab = "Social capital", 
  main = "Institutional level resources", cex = 0.6, 
  bty = "g", ticktype = "detailed", d = 2,
  clab = c("Urban","Pop"), adj = 1, font = 1.5))

#Zoom into to the middle for more clarity 
plotdev(xlim = c(3, 4), ylim = c(3, 5.5), 
         zlim = c(3, 3.8))

@@

#Reverse code attention variable 
```{r}
#Reverse code fundtion 
reverse <- function(x){x*-1- +8}

gali_att <- as.data.frame(lapply(gali %>%
                            select(starts_with("accel_ben_rank_")), reverse))

gali <- cbind(gali %>%
        select(-starts_with("accel_ben_rank_")), gali_att)

```{r}
mean_norm_att <- as.data.frame(lapply(gali %>%
                            select(starts_with("accel_ben_rank_")), mean_norm_minmax))

gali <- cbind(gali %>%
        select(-starts_with("accel_ben_rank_")), mean_norm_att)
```

@@

gali$attention_hc <- round(gali$accel_ben_rank_business_skills,2)

gali$attention_sc <- round(rowMeans(gali[,
                                  c('accel_ben_rank_network',
                                'accel_ben_rank_access_entreprene')],
                              na.rm=TRUE),2)

gali$attention_fc <-  round(rowMeans(gali[,
                                  c('accel_ben_rank_direct_funding',
                                'accel_ben_rank_access_investors')],
                              na.rm=TRUE),2)

@@

#Join all 3 datasets 
```{r}

gali_joined <- left_join(gali, gci, by = "country")

@@

#Mixed model analysis - Human capital
```{r}
fit0hc <- lmer(participated ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

fit1hc <- lmer(participated ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

summary(fit0hc)
summary(fit1hc)

fit00hc <- lmer(hr_tot ~  accel_ben_rank_business_skills + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

fit11hc <- lmer(hr_tot ~  accel_ben_rank_business_skills*EOSQ403 + (accel_ben_rank_business_skills|country), data = gali_joined, REML = F)

summary(fit00hc)
summary(fit11hc)

@@

#Mixed model analysis - Financial capital
```{r}
fit0fc <- lmer(participated ~   + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)

fit1fc <- lmer(participated ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)

fit2fc <- lmer(participated ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)

fit3fc <- lmer(participated ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, REML = F)

summary(fit0fc)
summary(fit1fc)
summary(fit2fc)
summary(fit3fc)

fit00fc <- lmer(capital_raised_tot ~   + (accel_ben_rank_direct_funding|country), data = gali_joined, REML = F)

fit11fc <- lmer(capital_raised_tot ~ accel_ben_rank_direct_funding*EOSQ425 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)

fit22fc <- lmer(capital_raised_tot ~ accel_ben_rank_direct_funding*EOSQ089 + (accel_ben_rank_direct_funding |country ), data = gali_joined, REML = F)

fit33fc <- lmer(capital_raised_tot ~ accel_ben_rank_direct_funding*DOMCREDITGDP + (accel_ben_rank_direct_funding |country), data = gali_joined, REML = F)

summary(fit00fc)
summary(fit11fc)
summary(fit22fc)
summary(fit33fc)

#Mixed model analysis - Social capital

```{r}
fit0sc <- lmer(participated ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)

fit1sc <- lmer(participated ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)

summary(fit0sc)
summary(fit1sc)

fit00sc <- lmer(equity_sources_tot ~ accel_ben_rank_network + (accel_ben_rank_network |country), data = gali_joined, REML = F)

fit11sc <- lmer(equity_sources_tot ~ accel_ben_rank_network*EOSQ109 + (accel_ben_rank_network | country), data = gali_joined, REML = F)

summary(fit00sc)
summary(fit11sc)
